Tensor anisotropy as a tracer of cosmic voids

### 2015-06-03 RefereeResponse.md

5. **I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions. 
    Based just on Fig. 1, they could be physical, but small, voids. We also no nothing of their extent 
    perpendicular to the plane of Fig. 1; we could just be looking of corners of much larger objects.**

    Response:
    - In Right panels of Fig. 1, the color of each void refers now the effective radius. The size can now be
      inferred from the figure. Small voids are indeed located inside sheets and filaments.

6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown
    in Fig. 2, and I would appreciate also  seeing a (FA, delta) 2D
    histogram, maybe with 1+delta on a log scale, which would help to
    clarify the  physical meaning of FA.**

    Response: 
    - We have included the new plot in Fig. 2. This shows that indeed
    the overdensity of zero is found at the highest Fractional Anisotropy.

### 2015-06-03 cosmic_voids.tex
solving issue #16 (major issue)

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{delta_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{FA_L1.pdf}  
  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.30\textheight]{FA_delta.pdf}

  \captionof{figure}{\small Density contrast (top) and Fractional
    Anisotropy (middle) with respect to the eigenvalue $\lambda_1$ 
    and with respect to each other (bottom) for each web scheme (T-Web, 
    continous lines. V-Web, dashed lines) calculated over all grid cells 
    in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin. This information is necessary to 
    define void boundaries in the watershed algorithm. The vertical lines 
    show the equivalent threshold values for the T-Web and V-web in order 
    to have voids composed by cells with Fractional Anisotrop equal or 
    less than $0.95$. This threshold on the eigenvalues does not influence 
    our computations. We show it as a guide to readers familiar with the
    order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

>>>>

%-------------------------------------------------------------------------
%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{figure*}
\centering

  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_delta.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{delta_L1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
  width=0.33\textwidth]{FA_L1.pdf}

  \captionof{figure}{\small Fractional Anisotropy  as a function of
    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
    density contrast (right) as a function of the
    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
    lines. V-Web, dashed lines). Thick central lines are the median
    and filled regions include $50\%$ of the cells in each bin. 
    The left panel we confirms that underdense regions can be
    identified with Fractional Anisotropy values less than $0.95$.
    For this reason we define voids to be composed by cells with
    Fractional Anisotropy equal or less than this value.
    In the middle and right panel we show the equivalent eigenvalue
    threshold for the T-Web and V-web corresponding to that
    Fractional Anisotropy. 
    This threshold on the eigenvalues does not influence 
    our computations. We show it as a guide to readers familiar with the
    order of magnitude expectation for this quantity.}
  \label{fig:L1_correlations}
